%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Rails developer} % Job title
    {\href{https://www.vworkapp.com/}{\underline{vWork}}} % Organization
    {Auckland, New Zealand} % Location
    {Sep. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Contributed extensively to the company's job scheduling web
                monolith, with a focus on optimization and code quality. }
        \item { Conducted multiple code refactoring efforts to promote code
                reuse and cleaner architecture, also removed unnecessary code
                reducing the codebase size significantly. }
        \item { Coded several optimization techniques, such as query
                refactoring, data caching or code profiling, among others, to
                improve the overall performance of the application. }
        \item { Upgrading Ruby/Rails/Webpack stacks for the 367K LOC monolith,
                including upgrade, replacement or removal of gems and packages. }
        \item { Constantly involved in test automation efforts within the IT
                team, along with promoting testing good practices in dev. team,
                related with test isolation and speed. }
        \item { Introduced tools to adhere coding standards (Rubocop/ESLint),
                also encouraging the rest of dev. team to follow them. }
        \item { Key developer, always supporting daily requirements from
                development, IT, testing and customer service teams. }
        \item { Integrating platform with 3rd party services like
                \href{https://www.hubspot.com/}{\underline{Hubspot}},
                \href{https://quickbooks.intuit.com/}{\underline{QuickBooks}},
                \href{https://www.myob.com}{\underline{MYOB}} or
                \href{https://www.xero.com}{\underline{Xero}}. }
        \item { Technologies used: Rails/React/GraphQL/PostgreSQL/Solr/Cassandra/RabbitMQ/Docker/AWS. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Rails developer} % Job title
    {\href{https://www.crunchbase.com/organization/meloncargo}{\underline{Meloncargo}}} % Organization
    {Remote} % Location
    {Oct. 2016 - Aug. 2108} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Integrating internal Rails system with third party services like
                \href{https://developers.mercadolibre.com/}{\underline{Mercado Libre API}} and
                \href{https://www.mercadopago.com.ar/developers/es/reference}{\underline{Mercado Pago API}} }
        \item { Development of \href{https://github.com/meloncargo/facturapi}{\underline{Facturapi}},
                a gem to interact with a SOAP service of \href{https://www.sii.cl}{\underline{SII}},
                the chilean taxes institution. }
        \item { Jenkins Install and config. with Docker as CI Service. }
        \item { Rails update to 5.x, including moving assets handling from react\_on\_rails to webpacker. }
        \item { Tech stack highlights: Elastic Search querying - React/Redux in frontend - Pusher notifications }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Rails developer} % Job title
    {Independent Contractor} % Organization
    {Remote} % Location
    {Apr. 2014 - Mar 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Worked with a wide range of clients, mostly from United States, through
                \href{https://www.upwork.com/freelancers/~0165692cc0b947512e}{\underline{Upwork}} platform.}
        \item { Developing for customers like
                \href{https://www.clouddentistry.com/}{\underline{Cloud Dentistry}},
                \href{https://www.clickfunnels.com/}{\underline{ClickFunnels}} or
                \href{https://martianinteractive.com/}{\underline{Martian Interactive}},
                to mention a few of them.}
        \item { Some tech stack: React frontend - CMS implementation - \\
                payment services integration with Stripe - I18n implement in front/back side}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Rails lead developer} % Job title
    {\href{https://4talent.cl/}{\underline{4Talent}}} % Organization
    {Santiago, Chile} % Location
    {Aug. 2012 - Mar. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { \href{https://trabajaenbci.cl/}{\underline{Recruitment platform}}
                built from scratch for \href{https://www.bci.cl/}{\underline{Bci Bank}}.}
        \item { Involved in requirement gathering, design of application and full stack development.}
        \item { Backend processing with sidekiq - Integration with third party API's -\\
                REST API development to support AngularJS frontend -
                Use of Elastic Search - File uploading to S3}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {} % Job title
    {Previous Experiences} % Organization
    {} % Location
    {Sep. 2007 - Jul. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { Rails developer in
        {\href{https://magazine.cranberrychic.com/}{\underline{Cranberry
        Chic}}}. Using BackboneJS frontend and REST API development for iPhone
        version of the app. }
        \item { Rails developer in Trifecta GIS (now known as
        {\href{https://www.t4spatial.com/}{\underline{T4 Spatial}}}). Maintenance
        and support of a Rails 3 application with Adobe Flex Frontend. }
        \item { Java developer in
        \href{https://www.continuumhq.com/}{\underline{Continuum}}. My first
        real project using Rails 2. }
        \item { Java/Flex developer in
        \href{https://www.linkedin.com/company/implementa-ti/}{\underline{Implementa
        TI}}. Using EJB/Hibernate }
        \item { Developer intern in
        \href{https://6sense.com/company/interplanet-sa/5ba611867c86660d3c6bb3fe}{\underline{Interplanet}}.
        Mostly testing of web apps and some roles as sysadmin of IBM Websphere
        servers }
      \end{cvitems}
    }

\end{cventries}
